Donor Responses to Civil Society Repression

### 2024-11-05 index.qmd
Convert to project

---
title: "Donor Responses to Civil Society Repression"
subtitle: "Chapter for the *Handbook of Political Control*"
date: 2024-11-04
author:
- name: Andrew Heiss
  affiliations: 
    - id: gsu
      name: Georgia State University
      department: Andrew Young School of Policy Studies, Department of Public Management and Policy
      address: "55 Park Place NE, #464"
      city: Atlanta
      region: GA
      country: USA
      postal-code: 30303
  orcid: 0000-0002-3948-3914
  url: https://www.andrewheiss.com
  email: aheiss@gsu.edu
  attributes:
    corresponding: true
- name: Suparna Chaudhry
  affiliation: Lewis and Clark College
  orcid: 0000-0003-3506-7590
  url: https://www.suparnachaudhry.com/
  email: schaudhry@lclark.edu
bibliography: references.bib
csl: csl/chicago-author-date.csl
toc: true
format:
  wordcount-html: 
    wordcount-banner: true
    shift-heading-level-by: 1
    theme: 
      - zephyr
      - html/custom.scss
    template-partials: 
      - html/title-metadata.html
    include-in-header:
      - text: |
          <style type="text/css">
          h2.hide {
            display: none;
          }
          </style>
    knitr:
      opts_chunk:
        dev: "ragg_png"
        dpi: 300

  # Nice PDF output
  hikmah-pdf:
    toc: false
    # Custom fonts
    mainfont: "Linux Libertine O"
    mainfontoptions:
      - "Numbers=Proportional"
      - "Numbers=OldStyle"
    sansfont: "Inter"
    mathfont: "Libertinus Math"
    # linestretch: 1.05

    knitr:
      opts_chunk:
        dev: "cairo_pdf"
params:
  wordcount: |
    <strong>{{< words-sum body-ref >}} total words</strong>: {{< words-body >}} in the body • {{< words-ref >}} in the references
language: 
  title-block-published: "Latest version"
---

>>>>

---
title: "Donor Responses to Civil Society Repression"
subtitle: "Chapter for the *Handbook of Political Control*"
date: 2024-11-04
author:
- name: Andrew Heiss
  affiliations: 
    - id: gsu
      name: Georgia State University
      department: Andrew Young School of Policy Studies, Department of Public Management and Policy
      address: "55 Park Place NE, #464"
      city: Atlanta
      region: GA
      country: USA
      postal-code: 30303
  orcid: 0000-0002-3948-3914
  url: https://www.andrewheiss.com
  email: aheiss@gsu.edu
  attributes:
    corresponding: true
- name: Suparna Chaudhry
  affiliation: Lewis and Clark College
  orcid: 0000-0003-3506-7590
  url: https://www.suparnachaudhry.com/
  email: schaudhry@lclark.edu
bibliography: references.bib
csl: csl/chicago-author-date.csl
params:
  wordcount: |
    <strong>{{< words-sum body-ref >}} total words</strong>: {{< words-body >}} in the body • {{< words-ref >}} in the references
---
